Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum disks

### 2018-11-07 paper_prd.tex
More work on the draft.

The models of KBHsSH we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}. The underlying theoretical framework is the Einstein-Klein-Gordon (EKG) field theory, describing a massive complex scalar field $\Psi$ minimally coupled to Einstein gravity. KBHsSH solutions are obtained by using the following ansatz for the metric and the scalar field~\cite{Herdeiro:2014a}
\begin{eqnarray}
%\begin{split}
\mathrm{d}s^2 &=& e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) +  e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2 
\nonumber \\ 
&-&  e^{2F_0}N\mathrm{d}t^2\,,
\label{metric}
\end{eqnarray}
\begin{eqnarray}
\Psi = \phi(r, \theta) e^{\mathrm{i}(m\varphi - \omega t)} \,,
%\end{split}
\end{eqnarray}
with $N = 1 - r_{\rm H}/r$, where $r_{\rm H}$ is the radius of the event horizon of the BH, and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$. Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.

@@

% %%%%%%%%%%%%%%%%%
% \subsection{Numerical method}
% %%%%%%%%%%%%%%%%%

% We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$. Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.

@@

@@

In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same morphological distribution of Figs.~\ref{models_I} and~\ref{models_II} but using, instead, a perimetral radial coordinate $R$, related to the Boyer-Lindquist radial coordinate according to $R = e^{F_2} r$. \tf{We need to justify why we introduce this new radial coordinate. What is the benefit? Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.} \sg{Discuss. I find that the 2D morphology in perimeteral coordintes might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \neq R_{\mathrm{H}} \neq 2M_{\mathrm{ADM}}$. I don't know if there are any kind of dependence on the angular momentum, as we don't two cases with the same value of the mass). I suppose this could help us to compare different models. In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you then please include some of this information in this paragraph?}

Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for all of our disk models around KBHsSH. First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$. As shown in~\cite{Abramowicz:1978}, constant angular momentum disks exhibit a maximum for $|\Delta W|$ when the spin parameter $a$ approaches 1. This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$. The models V, VI and VII violate that bound. This is related, as we see, with the maximum value of the specific enthalpy, pressure and magnetic pressure. \sg{The maximum value of these quantities increases with the total potential well $\Delta W$, irrespective of the value of the magnetisation.}

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
\hspace{-0.2cm}
\caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half). From left to right the columns correspond to models I, IV, and VII. The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
\tf{I think there is a lot of vertical space that we do not really need in these plots. To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now). I know the plot will not look squared, but that's fine.}\sg{Done.}
}
\label{comparison_mass_density}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
\hspace{-0.2cm}
\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate. \tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.} \sg{Done}}
\label{comparison_mass_density_peri}
\end{figure*}

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Distribution of angular momentum in the disk}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004,Gimeno-Soler:2017} and references therein). For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.

% We start by introducing the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
% \begin{equation}
% l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
% \end{equation}
% where $u^{\mu}$ is the fluid four-velocity.
% The relationship between $l$ and $\Omega$ is given by the equations
% \begin{equation}
% l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
% \end{equation}
% where we are assuming circular motion, i.e.~the four-velocity can be written as
% \begin{equation}
% u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
% \end{equation}

% The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}). In this work, for simplicity and to reduce the ample space of parameters, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}. This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.  \tf{We should explain/motivate why we change our approach in this paper.} Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
% \begin{equation}\label{eq:mb_ang_mom}
% l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}
% \end{equation}
% where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits. Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
% Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime. For prograde motion, the function has a minimum outside the event horizon. The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point. We show the proof of this statement in Appendix~\ref{ang_mom_appendix}. \tf{Is there an Appendix A?}.

% %%%%%%%%%%%%%%%%
% \subsection{Magnetized disks}
% %%%%%%%%%%%%%%%%

% To account for the magnetic flied in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}. We write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
% $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
% where $\nabla_{\mu}$ is the covariant derivative and
% \begin{equation}\label{eq:e-m_tensor}
% T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
% \end{equation}
% is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$. The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
% Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
% four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
% $b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
% and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
% \begin{equation}
% (\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
% \end{equation}
% where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
% \begin{equation}\label{eq:diff_ver}
% \partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
% \end{equation}
% where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.

% To integrate Eq.~\eqref{eq:diff_ver} we need to assume an equation of state (EOS). We assume a polytropic EOS of the form
% \begin{equation}\label{eq:eos_fluid}
% p = K \rho^{\Gamma},
% \end{equation}
% with $K$ and $\Gamma$ constants.
%  By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\widetilde{\rho h} = \mathcal{L} (\rho h)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
% \begin{eqnarray}
% \label{eq:eos_mag_tilde}
% \tilde{p}_{\mathrm{m}} &=& M \widetilde{\rho h}^q,
% \\
% p_{\mathrm{m}} &=& M \mathcal{L}^{q-1} (\rho h)^q,
% \end{eqnarray}
% where $M$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
% \begin{equation}\label{eq:final}
% W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}\rho h)^{q-1}=0,
% \end{equation}
% where $W \equiv \ln |u_t|$ stands for the (gravitational plus centrifugal) potential and  $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.

% We can also define the total energy density for the torus, $\rho_{\mathrm{T}}=-T^t_t + T^i_i$, and for the scalar field, $\rho_{\mathrm{SF}}=-(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i$. These are  given by
% \begin{eqnarray}\label{eq:torus_energy_density}
% \rho_{\mathrm{T}} &=&  \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
% \\
% \rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
% \end{eqnarray}

% %
% %\begin{equation}\label{eq:torus_energy_density}
% %\rho_{\mathrm{T}} = -T^t_t + T^i_i = \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
% %\end{equation}
% %and
% %\begin{equation}\label{eq:SF_energy_density}
% %\rho_{\mathrm{SF}} = -(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i = 2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
% %\end{equation}

% From the previous discussion it becomes apparent that the number of parameters defining the disk models is fairly large. In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$. Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH. With this information we can compute all relevant physical quantities.

% \tf{We should discuss a bit more the reason for this choice. If $l_{\rm ms}<l<l_{\rm mb}$ and $r_{\rm mb}<r_{\rm cusp}<r_{\rm ms}$ the disk is closed and has a centre and a cusp. If $l=l_{\rm mb}$ and $r_{\rm cusp}=r_{\rm mb}$ the disk has a centre and a cusp, and it is closed at infinity. The models we have built are the latter, right? I wonder if we should have built models not completely filling their Roche lobe, so that they had a finite size. In any case, a comment must be provided here.}

% \tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$. This is an important difference with respect to the work of~\cite{Vincent:2016}.}

% %%%%%%%%%%%%
% \section{Methodology}
% \label{procedure}
% %%%%%%%%%%%%

% \tf{Probably we do not need to have two subsections in this section, but just one. The description of the methodology is very
% poor now. It needs a lot of rewriting.}

% %%%%%%%%%%%%%%%%
% \subsection{Building the disks}
% %%%%%%%%%%%%%%%%

% To construct our models we first find the specific angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the minimum value of Eq.~\eqref{eq:mb_ang_mom} and the radial location of said minimum outside the event horizon, respectively. This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$, and $W_{\mathrm{in}} = 0$. Next, we can compute the gravitational plus centrifugal potential distribution as $W(r, \theta) \equiv \ln |u_t|$. Considering this, and that we can write the magnetic pressure at the centre as
% \begin{equation}
% p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = \frac{K}{\beta_{\mathrm{m_c}}},
% \end{equation}
% where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$. \tf{The previous sentence reads a bit strange.} Replacing this into Eq.~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
% \begin{equation}\label{eq:K_eq}
% W_{\mathrm{c}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\right) + \frac{q}{q-1}\frac{K/\beta_{\mathrm{m_c}}}{1 + \frac{\Gamma K}{\Gamma +1}} = 0.
% \end{equation}
% Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$. With this, we already have all we need in order to compute all the relevant physical quantities inside the disk.

% %%%%%%%%%%%%%%%%%
% \subsection{Numerical method}
% %%%%%%%%%%%%%%%%%

% We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$. Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.

% Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH. \tf{Describe.}

% <<<<<<< HEAD
% In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel). \tf{Describe this figure.}

% In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier. The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair. \tf{This trend is only satisfied for the unmagnetized models (top row) but not for the strongly magnetized models.}

% \tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only. Is this correct? Shouldn't we consider the entire stress-energy tensor from the fluid and the scalar field? Is this a valid approximation because we are in the test-fluid regime? What did~\cite{Vincent:2016} do?}

% \subsection{Comparison with KBHs}

% Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).

% %%%%%%%%%%%%%%%%%%
% \subsection{Magnetization profiles}
% %%%%%%%%%%%%%%%%%%

% The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}. The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter. \tf{Maybe there is an excessive number of cases for KBHs. Maybe it's enough to only include the four cases we have in Table III. We could always indicate in the main text the values that are reached for an extreme value of $a$ with seven 9. This will also simplify the presentation of this figure, where I don't like very much having lines and dots.} Here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization). However, there are differences between the two cases. For the enthalpy, the values of $h_{\mathrm{max}}$ reached for the KBHsSH are much higher than those of the KBH case. This fact tells us that, while the $w = \rho h \simeq \rho$ approximation (see \cite{Komissarov:2006} and \cite{Gimeno-Soler:2017}) is valid for magnetized flows ($\beta_{\mathrm{m_c}} \sim 1$) for reasonable values of the spin parameter ($a \sim 0.99$ or lower), that is not the case for KBHsSH. Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).

% Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}. The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$. As we can easily see, this condition is also fulfilled for the Kerr case, even $h \neq 1$ (with a slight deviation for very high spin parameter cases), but not quite for the KBHsSH cases.

% \sg{Include discussion about radial profiles.}

>>>>

The models of KBHsSH we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}. The underlying theoretical framework is the Einstein-Klein-Gordon (EKG) field theory, describing a massive complex scalar field $\Psi$ minimally coupled to Einstein gravity. KBHsSH solutions are obtained by using the following ansatz for the metric and the scalar field~\cite{Herdeiro:2014a}
\begin{eqnarray}
%\begin{split}
\mathrm{d}s^2 &=& e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) +  e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2 
\nonumber \\ 
&-&  e^{2F_0}N\mathrm{d}t^2\,,
\label{metric}
\end{eqnarray}
\begin{eqnarray}
\Psi = \phi(r, \theta) e^{\mathrm{i}(m\varphi - \omega t)} \,,
%\end{split}
\end{eqnarray}
with $N = 1 - r_{\rm H}/r$, where $r_{\rm H}$ is the radius of the event horizon of the BH, and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$. Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, where $a$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.

@@

@@

\begin{figure*}
\centering
\includegraphics[scale=0.1267]{figures/fig5_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.1267]{figures/fig5_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.1267]{figures/fig5_I__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.1267]{figures/fig5_VII__10.pdf}
\hspace{-0.2cm}
\caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half). From left to right the columns correspond to models I, IV, and VII. The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).}
\label{comparison_mass_density}
\end{figure*}

@@

In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same morphological distribution of Figs.~\ref{models_I} and~\ref{models_II} but using, instead, a perimetral radial coordinate $R$, related to the radial coordinate $r$ according to $R = e^{F_2} r$. This perimetral coordinate represents the proper length along the azimuthal direction, which constitutes a geometrically meaningful direction since it runs along the orbits of the azimuthal Killing vector field. Therefore, the proper size of a full $\phi$ orbit is given by $2\pi R$, i.e.~$R$ is the perimetral radius. The most salient feature of the morphologies shown in Figs.~\ref{models_peri_I} and~\ref{models_peri_II}, when comparing to those displayed in Figs.~\ref{models_I} and~\ref{models_II}, is the deformation of the disks in their innermost regions. In general, the deformations become larger the higher the BH spin and the closer the disk is to the horizon. Model III is the one showing the largest deformation, as $R_{\rm in}-R_{\rm H}$ attains the smallest value for this model. \tf{Check.} It is also worth noticing that the shape of the BH also changes when using the perimetral coordinate. While in the $r$ coordinate the horizon is spherical (cf.~Figs.~\ref{models_I} and~\ref{models_II}) in the perimetral coordinate $R$ is not always so. Moreover, the larger the value of $v_{\rm H}$, the more elliptic the horizon becomes, which in our sample corresponds to model III. \tf{Check.}

\sg{Discuss. I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \neq R_{\mathrm{H}} \neq 2M_{\mathrm{ADM}}$. I don't know if there are any kind of dependence on the angular momentum, as we don't two cases with the same value of the mass). I suppose this could help us to compare different models. In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you please include some of this information in here?}

Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for all of our disk models around KBHsSH. It is worth mentioning that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$. As shown in~\cite{Abramowicz:1978}, constant angular momentum disks arround Kerr BHs exhibit a maximum for $|\Delta W|$ when the spin parameter $a\rightarrow 1$. This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$. Models V, VI, and VII of our sample violate that bound. As a result, the maximum values of the fluid quantities for disks around KBHsSH are significantly larger than in the Kerr BH case. In both cases, these values increase as $|\Delta W|$ increases, irrespective of the magnetisation, as shown in Table~\ref{HBH_disk_parameters}.

%\begin{figure*}
%\centering
%\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
%\hspace{-0.4cm}
%\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
%\hspace{-0.4cm}
%\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
%\hspace{-0.2cm}
%\\
%\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
%\hspace{-0.4cm}
%\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
%\hspace{-0.4cm}
%\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
%\hspace{-0.2cm}
%\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate. \tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.} \sg{Done}}
%\label{comparison_mass_density_peri}
%\end{figure*}

@@

In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and two  values of the magnetisation parameter at the center ($10^{10}$, top row, and $10^{-10}$, bottom row). This figure shows that, for non-magnetised disks, the maximum of the total energy density of the disk $\rho_{\mathrm{T}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair. This trend disappears with increasing magnetisation, as the disk moves closer to the horizon in such case.

%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with Kerr BHs}
%%%%%%%%%%%%%%%%%%%%%

For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$. Our numerical approach can handle BH spins as large as $|a-1|=10^{-10}$ \tf{Check} but such extreme cases do not add further relevant information to our discussion. Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}. As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$. It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$. \tf{Describe further the table and the figures}. \tf{Mention that the horizon location is constant in perimetral coordinates irrespective of $a$.}
